### 2014-11-01 evaluation.tex
edits

\begin{table}
\setlength{\tabcolsep}{4pt}
{\sffamily \small
\begin{center}
\begin{tabular} {|l|r|r|r|r|r|r|r|}
\hline
{\bf Benchmark} & {\bf \#T} & {\bf EC} & {\bf CC} & {\bf SC} & {\bf RC} & {\bf MAV} & {\bf RR} \\
\hline
{LWW Reg} & 1 & 2 & 2 & 2 & 0 & 0 & 0 \\
{DynamoDB} & 1 & 3 & 1 & 2 & 0 & 0 & 0 \\
{Bank Account} & 1 & 1 & 1 & 1 & 1 & 0 & 1 \\
{Shopping List} & 1 & 2 & 1 & 1 & 0 & 0 & 0 \\
{Online store} & 4 & 9 & 1 & 0 & 2 & 0 & 1 \\
{Rubis} & 6 & 14 & 2 & 1 & 4 & 2 & 0 \\
{Microblog} & 5 & 13 & 6 & 1 & 6 & 3 & 1 \\
\hline
\end{tabular}
\end{center}
}
\caption{The distribution of classfied contracts. \#T refers to the number of tables in the application.}
\label{tab:ctrts}
\end{table}

@@

>>>>

\subsection{Contract Characteristics}

\begin{table}
\setlength{\tabcolsep}{4pt}
{\sffamily \small
\begin{center}
\begin{tabular} {|l|r|r|r|r|r|r|r|r|}
\hline
{\bf Benchmark} & {\bf LOC} & {\bf \#T} & {\bf EC} & {\bf CC} & {\bf SC} & {\bf RC} & {\bf MAV} & {\bf RR} \\
\hline
{LWW Reg} & 108 & 1 & 2 & 2 & 2 & 0 & 0 & 0 \\
{DynamoDB} & 126 & 1 & 3 & 1 & 2 & 0 & 0 & 0 \\
{Bank Account} & 155 & 1 & 1 & 1 & 1 & 1 & 0 & 1 \\
{Shopping List} & 140 & 1 & 2 & 1 & 1 & 0 & 0 & 0 \\
{Online store} & 340 & 4 & 9 & 1 & 0 & 2 & 0 & 1 \\
{Rubis} & 640 & 6 & 14 & 2 & 1 & 4 & 2 & 0 \\
{Microblog} & 659 & 5 & 13 & 6 & 1 & 6 & 3 & 1 \\
\hline
\end{tabular}
\end{center}
}
\caption{The distribution of classfied contracts. \#T refers to the number of
tables in the application. The columns 4-6 (7-9) represent operations
(transactions) assigned to this consistency (isolation) level.}
\label{tab:ctrts}
\end{table}

@@

The proof obligations associated with contract classfication is discarged
through the Z3 SMT Solver. In particular, the contract classification process
is completely performed compile time and has no overheads at runtime. Across
our benchmarks, classifying a contract took 11.5 milliseconds on average.
